---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip) [![Travis build status](https://travis-ci.org/ropenscilabs/ghrecipes.svg?branch=master)](https://travis-ci.org/ropenscilabs/ghrecipe)
 [![Coverage status](https://codecov.io/gh/ropenscilabs/ghrecipes/branch/master/graph/badge.svg)](https://codecov.io/github/ropenscilabs/ghrecipes?branch=master)



# ghrecipes

The goal of ghrecipes is to provide helper functions for usual GitHub _data mining_ tasks, well at least the ones that are usual or useful for us. :smile_cat: Please suggest and discuss new recipes in [the issues tracker!](https://github.com/ropenscilabs/ghrecipes/issues)

It uses[ GitHub V4 API](https://developer.github.com/v4/) queried thanks to the [`ghql` package](https://github.com/ropensci/ghql). Read more about [GitHub V4 API advantages here](https://developer.github.com/v4/#why-is-github-using-graphql). It then formats results using the [`jqr` package](https://github.com/ropensci/jqr), interface to [jq](https://stedolan.github.io/jq/). Read an intro to `jqr` power [here](http://www.carlboettiger.info/2017/12/11/data-rectangling-with-jq/). :rocket:

## Installation

You can install ghrecipes from GitHub with:


``` r
# install.packages("devtools")
devtools::install_github("ropenscilabs/ghrecipes")
```


## Examples

Don't miss conversations by your favorite developpers, or comments by your favorite [styling bot](https://github.com/lintr-bot). In that function, only the latest results are returned, and an issue can be a PR.

```{r}
ghrecipes::spy("lintr-bot", type = "Issue")
convos <- ghrecipes::spy("lintr-bot", type = "PullRequest")
knitr::kable(convos[1:10,])
```


## Use cases in the wild

* ["hrbrpkgs: list Bob Rudis' packages"](http://www.masalmon.eu/2018/03/04/hrbrpkgs/) by [Maëlle Salmon](https://github.com/maelle/).

* ["Lintr Bot, lintr's Hester egg"](http://www.masalmon.eu/2018/03/30/lintr-bot/) by [Maëlle Salmon](https://github.com/maelle/).

* ["Rectangling onboarding"](https://ropensci.org/blog/2018/04/26/rectangling-onboarding/) by [Maëlle Salmon](https://github.com/maelle/).

Add your use case to the list by [opening an issue](https://github.com/ropenscilabs/ghrecipes/issues/new)
!

## Nice words

<blockquote class="twitter-tweet" data-lang="ca"><p lang="en" dir="ltr">Both the package actual use and its source code have been very useful to me in understanding graphQL and the Github API. Thanks <a href="https://twitter.com/ma_salmon?ref_src=twsrc%5Etfw">@ma_salmon</a>!  <a href="https://t.co/i8KUAMGfsn">https://t.co/i8KUAMGfsn</a></p>&mdash; Christian Minich (@ChristianNolan) <a href="https://twitter.com/ChristianNolan/status/990686685682962434?ref_src=twsrc%5Etfw">29 d’abril de 2018</a></blockquote>


## Meta

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).

By participating in this project you agree to abide by its terms.
